### 2019-05-24 doc/chapters/towards_verifying.tex
rewriting require

\subsection{Rewriting require (funktioniert evtl?)}

>>>>

\subsection{Rewriting require}
Stainless output:
\begin{lstlisting}
  [Warning ] NumberType.scala:54:3: Could not extract tree in class:
             scala.this.Predef.require(Int64Impl.this.underlying.<=(
             math.this.BigInt.long2bigInt(9223372036854775807L)),
             "Number was too big for a int64, got: ".+(Int64Impl.this.underlying))
             (class scala.reflect.internal.Trees$Apply)
             require(underlying <= 9223372036854775807L,
\end{lstlisting}
This is, because Stainless does not support require with a second String parameter.
Removing this String fixes the error.
